R for Clinical Study Reports and Submission

### 2022-02-15 preface.Rmd
Add install and build guide to readme

  Yilong Zhang <<yilong.zhang@merck.com>>, Nan Xiao, Keaven Anderson

@@

```{r, results = "asis", echo = FALSE, message = FALSE}
contributors <- read.csv("contributors.csv", stringsAsFactors = FALSE, na.strings = "")
contributors$desc <- with(contributors, ifelse(is.na(username), name, paste0(name, " (\\@", username, ")")))
cat("  We are grateful for all the improvements brought by these contributors (in chronological order): ", sep = "")
cat(paste0(contributors$desc, collapse = ", "))
cat(".\n")
```

>>>>

  Yilong Zhang <<yilong.zhang@merck.com>>, Nan Xiao, Keaven Anderson, Yalin Zhu

@@

```{r, results = "asis", echo = FALSE, message = FALSE}
contributors <- read.csv("contributors.csv", stringsAsFactors = FALSE, na.strings = "")
contributors$desc <- with(contributors, ifelse(is.na(username), trimws(name), paste0(trimws(name), " (\\@", trimws(username), ")")))
cat("  We are grateful for all the improvements brought by these contributors (in chronological order): ", sep = "")
cat(paste0(contributors$desc, collapse = ", "))
cat(".\n")
```
